\cvsection{Elemental Projekts}
\begin{cventries}
    \cventry
        {Motivation: Part of my college assignments, gotta do them :p}
        {ProjektZirconium: A Banking server-client using gRPC and MongoDB}
        {C++17, gRPC, mongoDB}
        {Feb. 2020}
        {
            I built a gRPC and MongoDB based Client Server application using distributed transactions, it was a part of my Distributed Systems Assignment where we were asked to create a multi client, single server banking system using RPC/RMI.
            I chose to do this using c++, MongoDB and gRPC, and while I was at it, I decided to use Bazel Build System, So far I've been using CMake for building my c++ apps, but Bazel seems to have good potential for the future.
            GitHub actions was used to test the current build. I tried my best to document and present it on github.
            \url{https://github.com/satyajitghana/ProjektZirconium}
        }
    \cventry
        {Motivation : Internship Task}
        {ProjektCerium: A CLI Interface to OpenCV Operations in C++}
        {C++, OpenCV, Linux, GitHub CI/CD}
        {Mar. 2020}
        {Something i made for C++ Software Engineering Internship in Bangalore at Inkers Private Limited,
        The goal was to make a Cross Platform CLI tool to do various operations like recording video from webcam, applying filters on it, saving the video and then listing the video, while having a authentication feature.
        \url{https://github.com/satyajitghana/ProjektCerium}
        }
    \cventry
        {Motivation : Wanted to learn C++ and Compiler Design}
        {ProjektBarium: A Compiler for my Barium Language}
        {C++, Linux, Flex, Bison}
        {Dec. 2019 - March. 2020}
        {
        It's a toy compiler i made using Flex as parser, Bison as scanner and LLVM to generate IR Code and the binary executable. It can do simple function calls, variables, assignments, math ops, etc. The code is written in C++, both the parser and scanner as well. CMake is used to compile and run the program. see the GitHub repo for more details.
        \url{https://github.com/satyajitghana/ProjektBarium}
        }
    \cventry
        {Motivation : To create neural network from scratch in C++}
        {ProjektStrontium: A Neural Network from Scratch}
        {C++}
        {Aug 2019}
        {
        I implemented a simple feed forward Neural Network from scratch in C++, further work would include adding faster operations using Eigen and support for different activation functions and different backprop algorithms.
        \url{https://github.com/satyajitghana/ProjektStrontium}
        }
    \cventry
        {Motivation: CYNERGY (Coding Club) EndGame Hackathon Submisison}
        {ProjektIodine: A Marks Predcitor using ML on Browser}
        {Node.js, Tensorflow.js, Bootstrap, SASS, HTML5}
        {April 2019}
        {
            I used simple Linear Regression to predict the SEE Marks of the student given previous Term Tests Marks.
            \url{https://github.com/satyajitghana/ProjektIodine}
        }
    \cventry
        {Motivation: Need for a Local Network Media Centre for the entire house}
        {ProjektAstatine: Containerised Media, Cloud and Torrent Server}
        {Docker, Kubernetes, Plex, Samba, Ubuntu, Transmission}
        {Apr. 2020}
        {
            I always wanted easy share of files between laptops in my house and a storage space where i can dump my movies and watch in on Smart TV.
            Also wanted a Torrent Download Server where in can simply dump my .torrent files and it'll download and save it for me.
            \url{https://github.com/satyajitghana/ProjektAstatine}
        }
\end{cventries}